Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-10-21 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/BridgeDisappearing.pdf; improved our paper

We grow each original building and, as illustrated in 
\sect\ref{sec:DilationErosion}, simplify the grown building.
If some buildings become too close after these operations,
we aggregate them by adding bridges
(see for example \fig\ref{fig:GrowAndBridge}).
Following \citet{Stoter2009}, 
we define that two buildings are too close if their distance is less than
$\epsilon= 0.2\,\mathrm{mm}$ on map.
The real separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins
(see \fig\ref{fig:Buffer_ThreeKinds}b).
We merge the buffers that overlap each other.
The buildings intersect the same merged buffer 
are identified as a group of close buildings.
The corresponding original buildings 
are identified as a group of original close buildings.
For each pair of the original buildings in the same group,
we connect them by adding a line segment linking the nearest points.
The line segments for a group of original buildings may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a result, the line segments corresponding to the edges in the 
MST
are identified as bridges.
We aggregate the group of original buildings by adding these bridges.

@@

When buildings are grown and aggregated iteratively, bridges are added, 
and these bridges have a width of $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
As we aggregated all buildings that will be too close, 
we are able to guarantee that 
there is no pair of buildings 
which has separation distance less than $d_{\epsilon, t}$.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) Original buildings $p$, $q$, and~$r$.
		(b) Growing the original buildings with distance $\dtrm{G}$.
		(c) Buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
		using round joins.
		(d) Aggregating buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap each other in (c).
		(e) Growing the buildings in (d) with distance $\dtrm{G}$.
		(f) Buffering the grown buildings in (e) with distance 
		$d_{\epsilon,t}/2$ using round joins.
		(g) Aggregating buildings $p$, $q$ and~$r$ by adding bridges.
		(h) Growing the buildings in (g) with distance $\dtrm{G}$.
		(i) Buffering the grown buildings in (h) with distance 
		$d_{\epsilon,t}/2$ using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\epsilon, t} = \epsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least 
%$d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other 
%parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than 
%$d_{\epsilon, t}$ will be 
%aggregated via bridges.
%

@@

Both the erosion and line simplification may result in 
shrinking a building.
\fig\ref{fig:Shrink_Erosion} and \fig\ref{fig:Shrink_Simplification} show such 
examples respectively.
To avoid these kinds of shrinking,
for a building, we merge its shape at time $t$ 
and its shape at the immediately previous step (before $t$). 
For example, we generate a sequence of $10$ maps,
which means $t \in \{0.1, 0.2, \dots, 1\}$.
\fig\ref{fig:Shrink_Erosion}c shows the result at $t=0.6$.
In \fig\ref{fig:Shrink_Erosion}g, 
the dark-gray part included in the result at $t=0.6$,
but not in the result at $t=0.7$.
In other words, the result at $t=0.7$ shrinks at the dark-gray part.
To prevent the shrinking at $t=0.7$, we merge the result at $t=0.7$ with the 
result of the immediate previous step, i.e., $t=0.6$.
The merged result is shown in \fig\ref{fig:Shrink_Uniting}a.
Similarly, \fig\ref{fig:Shrink_Uniting}b shows the merged result of buildings 
in \fig\ref{fig:Shrink_Simplification}c 
and~\fig\ref{fig:Shrink_Simplification}h.

This merge can also avoid bridge's disappearing.
Recall that we always add a bridge linking the nearest points of 
two buildings in order to aggregate.
It can happen that 
the pair of nearest points change during growing.
\fig\ref{fig:NearestPoints} shows such an example.
For this example, at the beginning a bridge will added 
to link the pair of points marked by the squares. 
Later at some point, a bridge will be added 
to link the two points marked by the circles, 
while the first bridge will disappear.
This disappearing annoys users.
Fortunately, the merge operation makes the first bridge stay.

\begin{figure}[tb]
	\centering
	\includegraphics[]{NearestPoints}
	\caption{The nearest points between a pair of buildings	
		change because of growing. 
		The two squares and the two circles respectively mark
		the nearest points before and after growing.
	}
	\label{fig:NearestPoints}
\end{figure}

@@

@@

\subsection{Running time}
Suppose that our input has $n$ edges in total.
Operations like growing, dilation, erosion, merge, and clip 
cost time $O(n^2)$ \citep{Greiner1998Clipping,Palfrader2015}.
Although we iteratively aggregate (see \sect\ref{sec:Aggregate}),
it is unlikely that we need to repeat the aggregation more than 
twice.
Therefore, let us say that the iterative aggregation does not
take extra running time.
Simplifying polygons using Imai--Iri algorithm needs time
$O(n^3)$.
The improved version of Imai--Iri algorithm by 
\citet{Chan1996} does not help in our case
because we have more constraints when simplifying
(see \sect\ref{sec:ImaiIri}).
As a result, the simplification dominates our running time,
which is in $O(n^3)$.

@@

We produced a sequence of~$10$ maps,
i.e.,~$t \in \{0.1, 0.2, \dots, 1\}$.
This production costs~$668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:ExperimentalComparison}.
We counted the numbers of buildings in our results,
and compared them to the numbers calculated by T\"opfer's 
radical law (see \fig\ref{fig:NumberOfBuildings}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966} 
we used~$C_\mathrm{b2}$ and~$C_\mathrm{z3}$.
As a result, we computed the numbers according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where~$n_s=2{,}590$ is the number of buildings on start map
and~$n_t$ is the number of buildings on a map at scale~$1:M_t$.
According to \fig\ref{fig:NumberOfBuildings}, 
our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

@@

\begin{figure}[tb]
	\centering
	\includegraphics{NumberOfBuildings}
	\caption{A comparison of the numbers of building between our 
results and 
		T\"opfer's radical law.}
	\label{fig:NumberOfBuildings}
\end{figure}

@@

It is always interesting to know what is the quantity we should keep on a map.
We compared the numbers of buildings of our results, and it is consistent with 
the fractal law from \citet{Jiang2015}.
Another interesting problem is to compare the area of the buildings.
Eventually, our result is a set of settlement boundaries. An interesting 
problem is to compare our method with \citet{Chaudhry2008}.
Our method is supposed to provide a smooth transition between representations 
with individual buildings and representations with built-up areas, but the only 
way to verify that smoothness is achieved is to carry out a user survey where 
our approach is compared to non continuous generalization approaches.

>>>>

We grow each original building and, as illustrated in 
\sect\ref{sec:DilationErosion}, simplify the grown building.
If some buildings become too close after these operations,
we aggregate them by adding bridges
(see for example \fig\ref{fig:GrowAndBridge}).
Following \citet{Stoter2009}, 
we define that two buildings are too close if their distance is less than
$\varepsilon= 0.2\,\mathrm{mm}$ on map.
The real separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\varepsilon, t} = \varepsilon \cdot M_t.
\end{equation}

@@

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\varepsilon, t}/2$ using 
round joins
(see \fig\ref{fig:Buffer_ThreeKinds}b).
We merge the buffers that overlap each other.
The original buildings intersecting the same merged buffer 
are identified as a group of close buildings.
For each pair of the original buildings in the same group,
we connect them by adding a line segment linking the nearest points.
The line segments may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and 
each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a result, the line segments corresponding to the edges 
in the MST are identified as bridges.
We aggregate the group of original buildings 
by adding these bridges.

@@

When buildings are grown and aggregated iteratively, bridges are added, 
and these bridges have a width of $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
As we aggregated all buildings that will be too close, 
we are able to guarantee that 
there is no pair of buildings 
which has separation distance less than $d_{\varepsilon, t}$.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) Original buildings $p$, $q$, and~$r$.
		(b) Growing the original buildings with distance $\dtrm{G}$.
		(c) Buffering the grown buildings with distance 
		$d_{\varepsilon,t}/2$ 
		using round joins.
		(d) Aggregating buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap each other in (c).
		(e) Growing the buildings in (d) with distance $\dtrm{G}$.
		(f) Buffering the grown buildings in (e) with distance 
		$d_{\varepsilon,t}/2$ using round joins.
		(g) Aggregating buildings $p$, $q$ and~$r$ by adding bridges.
		(h) Growing the buildings in (g) with distance $\dtrm{G}$.
		(i) Buffering the grown buildings in (h) with distance 
		$d_{\varepsilon,t}/2$ using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\varepsilon, 
%t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\varepsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\varepsilon, t} = \varepsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\varepsilon, t}/2$
%(the distance between two buildings should be at least 
%$d_{\varepsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other 
%parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\varepsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\varepsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than 
%$d_{\varepsilon, t}$ will be 
%aggregated via bridges.
%

@@

Both the erosion and line simplification may result in 
shrinking a building.
\fig\ref{fig:Shrink_Erosion} and \fig\ref{fig:Shrink_Simplification} show such 
examples respectively.
To avoid these kinds of shrinking,
for a building, we merge its shape at time $t$ 
and its shape at the immediately previous step (before $t$). 
For example, we generate a sequence of $10$ maps,
which means $t \in \{0.1, 0.2, \dots, 1\}$.
\fig\ref{fig:Shrink_Erosion}c shows the result at $t=0.6$.
In \fig\ref{fig:Shrink_Erosion}g, 
the dark-gray part included in the result at $t=0.6$,
but not in the result at $t=0.7$.
In other words, the result at $t=0.7$ shrinks at the dark-gray part.
To prevent the shrinking at $t=0.7$, we merge the result at $t=0.7$ with the 
result of the immediate previous step, i.e., $t=0.6$.
The merged result is shown in \fig\ref{fig:Shrink_Uniting}a.
Similarly, \fig\ref{fig:Shrink_Uniting}b shows the merged result of buildings 
in \fig\ref{fig:Shrink_Simplification}c 
and~\fig\ref{fig:Shrink_Simplification}h.
This merge also avoids bridges' shrinking.
\fig\ref{fig:BridgeDisappearing} shows such an example.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{BridgeDisappearing}
	\caption{Avoiding shrinking resulted by moved bridges,
		where~$t_1=0.5$ and~$t_2=0.6$.
		(a) Original buildings.
		(b) Growing buildings with distance~$\dtrm[1]{G}$ and 
		dilating with~$d_{\varepsilon,t_1}/2$;
		buildings~$p$ and~$q$ are identified as in the same 
		group.
		(c) Aggregating~$p$ and~$q$	by adding a bridge.
		(d) Growing the (bridged) buildings in (c)
		with distance~$\dtrm[1]{G}$.
		(f) Growing original buildings with 
		distance~$\dtrm[2]{G}$ and 
		dilating with~$d_{\varepsilon,t_2}/2$;
		all the three buildings are in the same group
		(g) Aggregating	by adding bridges according to the MST.
		(h) Growing the bridged building in~(g)
		with distance~$\dtrm[2]{G}$. 
		The bridge in~(d) shrinks comparing to~(h).
		(e) Avoiding this shrinking at time~$t_2$ 
		by merging buildings of~(d) and~(h).
	}
	\label{fig:BridgeDisappearing}
\end{figure}

%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{NearestPoints}
%	\caption{The nearest points between a pair of buildings	
%		change because of growing. 
%		The two squares and the two circles respectively mark
%		the nearest points before and after growing.
%	}
%	\label{fig:NearestPoints}
%\end{figure}

@@

\subsection{Running time}
Suppose that our input has $n$ edges in total.
Operations like growing, dilation, erosion, merge, and clip 
cost time $O(n^2)$ \citep{Greiner1998Clipping,Palfrader2015}.
We iteratively aggregate in \sect\ref{sec:Aggregate}.
In the worst case, we need to repeat $O(n)$ times,
which increases our running time to $O(n^3)$.
It is unlikely that we need to repeat the aggregation more than 
twice, though.
Simplifying polygons using Imai--Iri algorithm needs time
$O(n^3)$.
The improved version of Imai--Iri algorithm by 
\citet{Chan1996} does not help in our case
because we have more constraints when simplifying
(see \sect\ref{sec:ImaiIri}).
As a result, the running time of our method is in $O(n^3)$.

@@

We produced a sequence of~$10$ maps,
i.e.,~$t \in \{0.1, 0.2, \dots, 1\}$.
This production costs~$668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:ExperimentalComparison}.
We counted the numbers of buildings in our results,
and compared them to the numbers calculated by T\"opfer's 
radical law (see \fig\ref{fig:NumberOfBuildings})
and our \emph{areal law}.
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966} 
we used~$C_\mathrm{b2}$ and~$C_\mathrm{z3}$.
As a result, we computed the numbers according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where~$n_s=2{,}590$ is the number of buildings on start map
and~$n_t$ is the number of buildings on a map at scale~$1:M_t$.
For the areal law, we argue that the number of buildings in a 
unit area on map should be fixed, which leads to
\[
n'_t=n_\mathrm{s}\left( \frac{M_\mathrm{s}}{M_t}\right) ^2.
\]
According to \fig\ref{fig:NumberOfBuildings}, 
our numbers decrease faster than 
the numbers of both the radical law and the areal law.

@@

\begin{figure}[tb]
	\centering
	\includegraphics{NumberOfBuildings}
	\caption{A comparison of the numbers of buildings 
		between our result, areal law, 
		and T\"opfer's radical law.}
	\label{fig:NumberOfBuildings}
\end{figure}

@@

It is always interesting to know the quantity we should keep on 
a map.
We compared the numbers of buildings, and it is more consistent 
with the areal law than T\"opfer's radical law.
Another interesting problem is to compare the area of the buildings.
Eventually, our result is a set of settlement boundaries. An interesting 
problem is to compare our method with \citet{Chaudhry2008}.
Our method is supposed to provide a smooth transition between representations 
with individual buildings and representations with built-up areas, but the only 
way to verify that smoothness is achieved is to carry out a user survey where 
our approach is compared to non continuous generalization approaches.
